TOP10 COMPONENT ANALYSIS - PovertyChild

### 2024-01-09 minos/testing/S7_comp_change_boxplot_child.Rmd
Created notebook for component boxplots of top 10 percent

---
params:
    out_path: '' # default arguments. specify others in command line.
    intervention: ''
title: "`r paste(params$file_path, ' ', params$intervention, ' ANALYSIS')`"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

```{r}
out.path.batch <- here::here('output', params$out_path)
intervention <- params$intervention

@@

```{r}
# S7_pathway_change_byGroup <- function(base.batch, int.batch, group.var, var) {
#   base.sub <- base.batch %>%
#     select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var)) %>%
#     group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
#     count() %>%
#     group_by(time, run_id, .data[[group.var]]) %>%
#     mutate(total = sum(n),
#            base_prop = n / total) %>%
#     select(-n, -total)
#
#   int.sub <- energy.batch %>%
#     select(pidp, time, run_id, equivalent_income, all_of(group.var), all_of(var)) %>%
#     group_by(time, run_id, .data[[group.var]], .data[[var]]) %>%
#     count() %>%
#     group_by(time, run_id, .data[[group.var]]) %>%
#     mutate(total = sum(n),
#            int_prop = n / total) %>%
#     select(-n, -total)
#
#   combined <- merge(base.sub, int.sub, by = c('time', 'run_id', group.var, var))
#   combined$prop_diff <- combined$int_prop - combined$base_prop
#
#   combined[[var]] <- as.factor(combined[[var]])
#
#   ggplot(data = combined, aes(x = time, y = prop_diff, group = .data[[var]], color = .data[[var]])) +
#     geom_smooth() +
#     facet_wrap(~ .data[[group.var]], nrow=1) +
#     theme(axis.title.x = element_blank(),
#           axis.text.x = element_blank(),
#           axis.ticks.x = element_blank())
# }
```

>>>>

---
title: "TOP10 COMPONENT ANALYSIS - ChildUplift"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

```{r}
# out.path.batch <- here::here('output', params$out_path)
# intervention <- params$intervention

out.path.batch <- here::here('output', 'SIPHER7')
intervention <- 'hhIncomeChildUplift'

@@

```{r}
# select only top 10% of equivalent income increases
base.sub <- base.batch %>%
  select(pidp, time, equivalent_income) %>%
  rename(baseline = equivalent_income)

int.sub <- int.batch %>%
  select(pidp, time, equivalent_income) %>%
  rename(intervention = equivalent_income)

merged <- merge(x = base.sub,
                y = int.sub,
                by = c('pidp', 'time'))

rm(base.sub, int.sub)

top10p <- merged %>%
  mutate(diff = intervention - baseline) %>%
  group_by(pidp) %>%
  summarise(sum_diff = sum(diff)) %>%
  filter(sum_diff > quantile(sum_diff, .9))

rm(merged)

print(paste0('Top 10% of improvers: n = ', nrow(top10p)))

base.batch <- base.batch %>%
  filter(pidp %in% unique(top10p$pidp))
int.batch <- int.batch %>%
  filter(pidp %in% unique(top10p$pidp))

rm(top10p)
```

### 2024-01-09 minos/testing/S7_comp_change_boxplot_livWage.Rmd
Created notebook for component boxplots of top 10 percent

---
title: "TOP10 COMPONENT ANALYSIS - ChildUplift"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

out.path.batch <- here::here('output', 'SIPHER7')
intervention <- 'hhIncomeChildUplift'

>>>>

---
title: "TOP10 COMPONENT ANALYSIS - Living Wage"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

out.path.batch <- here::here('output', 'SIPHER7')
intervention <- 'livingWageIntervention'

### 2024-01-09 minos/testing/S7_comp_change_boxplot_pov.Rmd
Created notebook for component boxplots of top 10 percent

---
title: "TOP10 COMPONENT ANALYSIS - Living Wage"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

out.path.batch <- here::here('output', 'SIPHER7')
intervention <- 'livingWageIntervention'

>>>>

---
title: "TOP10 COMPONENT ANALYSIS - PovertyChild"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

out.path.batch <- here::here('output', 'SIPHER7')
intervention <- 'hhIncomePovertyLineChildUplift'
